APPM report - Draft

### 2022-12-01 paper_version/main.tex
incorporate the latest comments

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
\setlength\arrayrulewidth{0.7pt}
\usepackage{authblk}
\usepackage{soul}

@@

Our approach is inspired by \cite{degond_2012}, but goes beyond that work in various directions:
\begin{itemize}
    \item we supplement the Maxwell-Euler system by inter-species friction;
    \item we extend the spatially 1D scheme of \cite{degond_2012} to three spatial dimensions using discrete exterior calculus (DEC) for Maxwell's equations combined with a low-order finite volume method for Euler's equations;
    \item we propose an essential stabilization in non-conducting regions;
    \item we introduce suitable boundary conditions for the electromagnetic fields at a spatial truncation boundary.
\end{itemize}

We stay close to \cite{degond_2012} in terms of discretization in time by semi-implicit time-stepping and by restricting to a cylindrical geometry shown in Fig. \ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical scheme proposed in this paper can in principle be adapted to geometric situations much more general than that of Fig. \ref{fig:domain_geometry}. However, one may encounter subtle problems in defining proper mesh duality as we need it in Section \ref{sec:mesh-duality}. Thus, for the sake of simplicity of presentation we forgo geometric generality.

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the PDE system changes its type \footnote{from hyperbolic to a mixed type}. This poses a challenge for simulations in settings encompassing different regimes. Singularly perturbed problems occur in many physical models, e.g. vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}. It is desirable that numerical schemes are valid for all ranges of scaled parameters. These schemes are then said to be \emph{asymptotic-preserving} (AP). The concept is sketched by the commutative diagram in \cite{jin_1999}. We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$ by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g. mesh size. The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. For more details about AP schemes, see \cite{jin_2010, degond_2017} for comprehensive reviews.

The content of this paper is organized as follows. In Section 2, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A reformulation of Maxwell's equations in the insulating region is then presented. Section 3 is devoted to the spatial discretization. The concept of primal-dual meshes is introduced based on which FIT and FVM are applied. We discuss the fully-discretized AP scheme in Section 4 and do numerical experiments in Section 5.

@@

\section{Plasma model}
\begin{comment}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations. Maxwell's equations are involved to describe their induction of and interaction with electromagnetic fields.

After rescalling all the variables with respect to the prescribed reference units, the Debye length $\lambda_D$, characterizing the charge screening ability of the plasma, would pop up and its zero limit, which is what we called \emph{quasi-neutral limit}, is of great interest, since the limit model largely simplifies the system and in many cases the accuracy of the assumption is satisfactory enough.

In this section, the multi-species Maxwell-Euler equations with collision term is introduced first, followed by detailed rescalling procedure. The quasi-neutral model will be make clear by letting the rescaled Debye length $\lambda$ go to zero. Afterwards, a set of boundary conditions are presented and its validity to both non-limit and limit model is discussed. Finally, we would like to present a reformulation of the system which would be crucial to the stability of the numerical scheme.
\end{comment}

\begin{comment}
In this work, we discuss and implement the so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, i.e. when the \emph{Debye length} goes to zero. The dimensionless form of the Euler-Maxwell equations is parameterized by the rescaled Debye length $\lambda$ whose vanishing limit alters the mathematical nature of the equations. To be more concrete, the non-limit model ($\lambda = \mathcal{O}(1)$) is hyperbolic where information spreads with a finite speed whereas the limit model ($\lambda \rightarrow 0$) becomes elliptic, and any changes immediately influence the whole domain. In other words, the perturbation of $\lambda$ in the Maxwell-Euler system poses a singular perturbation problem. Such switching makes it difficult to handle both models in a single implementation framework, which, however, is desired in many cases where both models coexist in the computational domain. Now comes the concept of \emph{asymptotic-preserving}(AP) scheme. We turn to the celebrated commuting diagram Fig. \ref{fig:commuting_diagram_ap} for illustration.\todo{add illustration of AP schemes}.

The other emphasis of this work is the development of a 3D discretization framework for the Maxwell-Euler system. The key ingredient is the combination of the finite volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for Maxwell's equations. The latter one is usually treated as a generalization to Yee's scheme \citep{yee_1966} or FDTD. The advantage of the FVM-FIT framework lie in the \emph{discrete exterior calculus} (DEC) nature of FIT and straightforward coupling of both systems through the primal-dual mesh pair. These would be made clear in the corresponding sections.

\todo{add previous work on AP schemes, FIT, plasma simulation}.

The content of this paper is organized as follows. In Section 2 we introduce the full Maxwell-Euler model for plasmas, followed by the rescaling procedure which is crucial to define the rescaled Debye length $\lambda$ and to identify its limiting behavior. In the meantime, it is essential to discuss what boundary conditions are appropriate for this singular perturbation problem. Section 3 is then dedicated to a brief introduction about \cite{degond_2012} based on which our work is extended. In Section 4, we first discuss our FVM-FIT framework in details, especially how the unknowns are assigned on the staggered meshes and the boundary treatment in 3D case. Afterwards, the full discretization scheme is presented. Special care shall be taken to the treatment of boundary conditions and insulator part of the domain as $\lambda \rightarrow 0$, which is crucial to make the scheme AP. A numerical experiment for a 3D cylindrical domain is presented in Section 5 where we want to demonstrate the capability of our scheme in dealing with both non-neutral and quasi-neutral regimes of plasmas.

\begin{figure}
    \centering
    \begin{tikzpicture}
    \node (nw) {\Large $P^\lambda_h$};
    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
    \node (sw) [below=of nw]{\Large $P^0_h$};
    \node (se) [right=3cm of sw]{\Large $P^0$};
    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
    \draw[->] (nw.east)  --  (ne.west) ;
    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
    \draw[->] (nw.south) -- node {} (sw.north);
    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
    \end{tikzpicture}
    \caption{Commuting diagram of AP schemes}
    \label{fig:commuting_diagram_ap}
\end{figure}
\end{comment}

\subsection{The Maxwell-Euler System}
Plasmas consist of electrically charged and neutral species that may be treated as gases. That is, they may be described by the Navier-Stokes equations augmented with source terms for species generation (ionization, recombination), forces (Lorentz force and interspecies friction), and energy (thermal relaxation among species, radiative heat transfer, Ohmic heating). For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.

The Maxwell's equations in SI units read
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
\end{subequations}
where the involved quantities are magnetic flux density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, electric field intensity $\mathbf{E}[\frac{\text{V}}{\text{m}}]$, electric induction $\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, magnetic field intensity $\mathbf{H}[\frac{\text{A}}{\text{m}}]$, electric current density $\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and electric charge density $\rho[\frac{\text{C}}{\text{m}^3}]$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous media in vacuum. We consider the linear constitutive relations 
\begin{equation} \label{equ:material_law}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation}
where $\varepsilon_0[\frac{\text{F}}{\text{m}}]$ and $\mu_0[\frac{\text{N}}{\text{A}^{2}}]$ are vacuum permittivity and permeability of medium. By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that the well-posedness requires the charge conservation equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.

Each species in a plasma can be modelled as a compressible fluid by a set of the Euler equations, which additionally includes electromagnetic forces as well as other processes, e.g. collisions and recombination. The generic expressions are
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{pmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{pmatrix}
    =
    \begin{pmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}
    +
    \begin{pmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{pmatrix}.
\end{align}
The subscript $*\in \{e, i, \cdots\}$ represents the indices for electron, ions and other species. The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  charge number $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$. All the species are assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side takes into account the Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.

For the sake of simplicity, we only consider ion-electron collision in this work, but extension to more species is straightforward. Such collisions can be well modelled by friction terms (\citep[][sec. 5.6.2]{chen2016})
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which is the collision force acting on electrons. ln$\Lambda$ is called the \emph{Coulomb logarithm} and is usually taken as a constant \cite{chen2016}. Because of the conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other effects, e.g. ionization and recombination, are not considered. For full details about the modeling of these physical processes, readers are referred to \cite{fuchs_2021}.

@@

\subsection{Rescaling} \label{sec:rescaling}
In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form. In this part, the rescaling procedure mostly follows that of \cite{degond_2017}.

First, a reference value for each quantity, e.g. the characteristic length and time scale, is prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$. Together with the physical parameters, i.e. permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\text{neutron},\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
\setlength\arrayrulewidth{0.7pt}
\usepackage{authblk}
\usepackage{soul}
%\usepackage{showlabels}
\usepackage{multirow}

@@

Our approach is inspired by \cite{degond_2012}, but goes beyond that work in various directions:
\begin{itemize}
    \item We supplement the Maxwell-Euler system by inter-species friction terms.
    \item We extend the spatially one-dimensional scheme of \cite{degond_2012} to three spatial dimensions using discrete exterior calculus (DEC) to discretize Maxwell's equations combined with a low-order finite volume method for Euler's equations.
    \item We propose a stabilization in non-conducting regions which is essential for the efficacy of our method.
\end{itemize}

We stay close to \cite{degond_2012} in terms of discretization in time employing semi-implicit time-stepping. We also base our considerations on the model geometry shown in Fig. \ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical scheme proposed in this paper can in principle be adapted to geometric situations much more general than that of Fig. \ref{fig:domain_geometry}. However, one may encounter subtle problems in defining proper dual meshes as we need it in Section \ref{sec:mesh-duality}. Thus, for the sake of simplicity of presentation we forgo geometric generality.

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the PDE system changes its type\footnote{from hyperbolic to a mixed type}. This poses a challenge for simulations in settings encompassing different regimes. Singularly perturbed problems occur in many physical models, e.g. vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}. It is desirable that numerical schemes are valid for all ranges of scaled parameters. These schemes are then said to be \emph{asymptotic-preserving} (AP). We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g. the mesh size, see also the illustration by a commuting diagram in \cite[][fig. 1]{jin_2010}. The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are referred to the comprehensive reviews in \cite{jin_2010, degond_2017} for more details about AP schemes.

The content of this paper is organized as follows: In Section 2, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A reformulation of Maxwell's equations in the insulating region is then presented. Section 3 is devoted to the spatial discretization. The concept of primal-dual meshes is introduced based on which FIT and FVM are applied. We discuss the fully-discretized AP scheme in Section 4 and do numerical experiments in Section 5.

@@

\section{Plasma model}

\subsection{The Maxwell-Euler System}
Plasmas consist of electrically charged and neutral particle species that can be treated as fluids. That is, they may be described by the Navier-Stokes equations augmented with source terms for species generation (ionization, recombination), forces (Lorentz force and interspecies friction), and energy (thermal relaxation among species, radiative heat transfer, Ohmic heating). For more details on fluid models of plasmas, see \cite{chen2016, remi_2014}.

The electromagnetic effects in plasmas are governed by Maxwell's equations, which Maxwell's equations in SI units read
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
\end{subequations}
where the involved quantities\footnote{SI units in square brackets.} are the magnetic flux density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, the electric field $\mathbf{E}[\frac{\text{V}}{\text{m}}]$, the electric displacement field $\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, the magnetic field $\mathbf{H}[\frac{\text{A}}{\text{m}}]$, the electric current density $\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and the electric charge density $\rho[\frac{\text{C}}{\text{m}^3}]$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous media in vacuum, which amounts to relying on the linear constitutive relations (namely, material laws):
\begin{equation} \label{equ:material_law}
    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu\mathbf{H}, 
\end{equation}
where $\epsilon[\frac{\text{F}}{\text{m}}]$ and $\mu[\frac{\text{N}}{\text{A}^{2}}]$ are the permittivity and permeability and assumed to be constant in this paper. By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that (\ref{equ:maxwell_ampere}) and (\ref{equ:maxwell_gauss_D}) implies the charge conservation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, by taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.

Each species in a plasma can be modelled as a compressible fluid by a set of Euler equations, which additionally includes electromagnetic forces as well as other processes, e.g. collisions and recombination. The generic expressions are
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{pmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{pmatrix}
    =
    \begin{pmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}
    +
    \begin{pmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{pmatrix}.
\end{align}
The subscript $*\in \{e, i, \cdots\}$ represents the indices for electron, ions and other species. The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  charge number $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$. All the species are assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side takes into account the Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.

For the sake of simplicity, we only consider ion-electron collision in this work, but extension to more species is straightforward. Such collisions can be well modelled by friction terms (\citep[][sec. 5.6.2]{chen2016})
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which is the collision force acting on electrons. ln$\Lambda$ is called the \emph{Coulomb logarithm} and is usually taken as a constant \cite{chen2016}. Because of the conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other effects, e.g. ionization and recombination, are not considered. For full details about the modeling of these physical processes, readers are referred to \cite[][sec. 3.2]{fuchs_2021}.

@@

\subsection{Rescaling} \label{sec:rescaling}
In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form. In this part, the rescaling procedure mostly follows that of \cite[][sec. 2.2]{degond_2017}.

First, a reference value for each quantity, e.g. the characteristic length and time scale, is prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the reference pressure is set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the reference value for the specific total energy and enthalpy is set to $\overline{u}^2$. Also taking into account the physical constants, i.e. the reference permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless parameters:
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

By abuse of notation, the dimensionless quantities have the same symbol as the original quantities. For the sake of simplicity, we neglect ionization and recombination but retain collision terms, i.e. $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{subequations}
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{D} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{H} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix} +
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{pmatrix}, \label{equ:euler_rescalling}
\end{align}
\end{subequations}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). \label{equ:rescaling_friction}
\end{equation}

 Assumptions can be made to reduce the number of dimensionless parameters. Following \cite[][sec. 2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$. Also, it is assumed that $\eta$ and $\beta$ are of order one and $\xi$ has the same magnitude as $\lambda$.

Special treatment is needed for the collision term. One could argue that the occurrence of $\lambda^{-1}$ in (\ref{equ:rescaling_friction}) could lead to singular perturbation of the Euler system as $\lambda \rightarrow 0$. However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$. From the physical viewpoint, the shielding effect characterized by the rescaled Debye length $\lambda$ makes the impact parameter no larger than $\lambda$. The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \cite[][pp. 144-148]{frank_1972}. Therefore, we eliminate the perturbation parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor $\alpha^{\text{coll}}$ of the collision term constant throughout the simulation.

\begin{remark}
    The case when there is an asymptotic parameter at the denominator of the friction term is of interest, too. Such problem is called relaxation limit, see \cite{peng_2011, wasiolek_2016, Li_2021, Chen_2000}.
\end{remark}

In summary, we make the following choices\cite[][sec 2.2]{degond_2017}
\begin{align*}
    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
\end{align*}
